Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-01-09 WSSSPE4_report/survey_details.tex
Remove borders on Survey Figures
All figures are now designated rev(used)
moving and shrinking figures
minor comments
playiung with figure spacing

@@

@@

@@

>>>>

%Figures have been inserted with little/no formatting.  
%Figures are in *.png but can be remade to other formats 
%\todo{Place 3 figures in 1 row with Latex}
%\begin{figure}[h!]
%\includegraphics[width=0.3\textwidth]{figures/SurveyFig1rev}
%\caption{The plenary sessions had a good mix of topics and speakers.
%\label{fig:SFig1}}
%\end{figure}
%\begin{figure}[h!]
%\includegraphics[width=0.3\textwidth]{figures/SurveyFig2rev}
%\caption{The balance was right between talks, panels, and lightning talks.
%\label{fig:SFig2}}
%\end{figure}
%\begin{figure}[h!]
%\includegraphics[width=0.3\textwidth]{figures/SurveyFig3rev}
%\caption{There was sufficient time for discussion.
%\label{fig:SFig3}}
%\end{figure}

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{figures/SurveyFig1rev}
  \caption{The plenary sessions had a good mix of topics and speakers.\label{fig:SFig1}}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{figures/SurveyFig2rev}
  \caption{The balance was right between talks, panels, and lightning talks.\label{fig:SFig2}}
\endminipage\hfill
\minipage{0.35\textwidth}%
  \includegraphics[width=\linewidth]{figures/SurveyFig3rev}
  \caption{There was sufficient time for discussion.\label{fig:SFig3}}
\endminipage
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=0.4\textwidth]{figures/SurveyFig4rev}
\caption{What part of the meeting was the most valuable?
\label{fig:SFig4}}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{figures/SurveyFig5rev}
\caption{Would you be interested in joining a professional society focused around the topics of WSSSPE?
\label{fig:SFig5}}
\end{figure}

@@

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{figures/SurveyFig6rev}
\caption{Will you be part of a working group  with colleagues going forward  on a topic addressed at WSSSPE?
\label{fig:SFig6}}
\end{figure}
